---
title: "Exploratory Data Analysis"
output: html_notebook
---

This notebook is just an exploratory data analysis to begin with.

```{r setup}
library(readr)
library(dplyr)
library(ggplot2)

options(scipen = 999)

train <- read_csv(file.path(here::here(), "data/external/train.csv"))
```

```{r a first look}
train %>% head
```

Lets plot the distribution of house prices.

```{r house price distribution}
train %>%
    ggplot(aes(x = SalePrice)) +
    geom_histogram()
```

We will be assessed based upon the RMSE between the logarithm of the predicted value and the logarithm of the observed sales price. Therefore, we probably want to be building a model on the log score.

Lets see the plot above of house price distribution on the log scale.

```{r house price distribution log scale}
train %>%
    ggplot(aes(x = SalePrice)) +
    geom_histogram() +
    scale_x_log10()
```

How many houses are there?

```{r}
nrow(train)
```

To begin with, I'll just have a look at some variables that I expect to be key based upon my knowledge on what influences the price of a house.

These are:
* Number of bedrooms/rooms
* Amount of land
* Location (urban/rural)
* House or flat
* Condition of the house
* House Age


