---
title: "Model Analysis"
output: html_notebook
---

```{r set up}
library(readr)
library(dplyr)
library(ggplot2)
library(arm)

options(dplyr.summarise.inform = FALSE)

model <- readRDS(file.path(here::here(), "models", "mixed_effects_model.rds"))

train <- read_csv(file.path(here::here(), "data/interim/train.csv"))
train <- train %>%
  mutate(
    predLogSalePrice = predict(model, train),
    resid = logSalePrice - predLogSalePrice
  )
```

In this notebook I take my predictions from the previous script and analyse them to see where they are weak and could be improved.

Lets take a look at residuals to do with the interior areas of the property.

```{r interior areas residual plots}
binnedplot(train$HighQualFinSF, train$resid)
binnedplot(train$LowQualFinSF[train$LowQualFinSF != 0], train$resid[train$LowQualFinSF != 0])
binnedplot(train$BsmtFinSF_1[train$BsmtFinSF_1 != 0], train$resid[train$BsmtFinSF_1 != 0])
binnedplot(train$BsmtFinSF_2[train$BsmtFinSF_2 != 0], train$resid[train$BsmtFinSF_2 != 0])
binnedplot(train$BsmtFinSF_3[train$BsmtFinSF_3 != 0], train$resid[train$BsmtFinSF_3 != 0])
binnedplot(train$BsmtFinSF_4[train$BsmtFinSF_4 != 0], train$resid[train$BsmtFinSF_4 != 0])
binnedplot(train$BsmtFinSF_5[train$BsmtFinSF_5 != 0], train$resid[train$BsmtFinSF_5 != 0])
binnedplot(train$BsmtFinSF_6[train$BsmtFinSF_6 != 0], train$resid[train$BsmtFinSF_6 != 0])
```

Lets take a look at the residuals to do with how much land the property has.

```{r land residual plots}
binnedplot(train$LotArea, train$resid)
train %>%
  group_by(LotShape) %>%
  summarise(
    number = n(),
    mean_resid = mean(resid),
    se_resid = sd(resid)/sqrt(n())
  )
```

Lets take a look at the residuals to do with the property location

```{r location residuals}
train %>%
  group_by(MSZoning) %>%
  summarise(
    number = n(),
    mean_resid = mean(resid),
    se_resid = sd(resid)/sqrt(n())
  )

train %>%
  group_by(Neighborhood) %>%
  summarise(
    number = n(),
    mean_resid = mean(resid),
    se_resid = sd(resid)/sqrt(n())
  )

train %>%
  group_by(AdjacentArterialStreet) %>%
  summarise(
    number = n(),
    mean_resid = mean(resid),
    se_resid = sd(resid)/sqrt(n())
  )

train %>%
  group_by(AdjacentFeederStreet) %>%
  summarise(
    number = n(),
    mean_resid = mean(resid),
    se_resid = sd(resid)/sqrt(n())
  )

train %>%
  group_by(Within200FtOfNSRailroad) %>%
  summarise(
    number = n(),
    mean_resid = mean(resid),
    se_resid = sd(resid)/sqrt(n())
  )

train %>%
  group_by(AdjacentToNSRailroad) %>%
  summarise(
    number = n(),
    mean_resid = mean(resid),
    se_resid = sd(resid)/sqrt(n())
  )

train %>%
  group_by(NearPosOffsiteFeature) %>%
  summarise(
    number = n(),
    mean_resid = mean(resid),
    se_resid = sd(resid)/sqrt(n())
  )

train %>%
  group_by(AdjacentPosOffsiteFeature) %>%
  summarise(
    number = n(),
    mean_resid = mean(resid),
    se_resid = sd(resid)/sqrt(n())
  )

train %>%
  group_by(Within200FtOfEWRailroad) %>%
  summarise(
    number = n(),
    mean_resid = mean(resid),
    se_resid = sd(resid)/sqrt(n())
  )

train %>%
  group_by(AdjacentEWRailroad) %>%
  summarise(
    number = n(),
    mean_resid = mean(resid),
    se_resid = sd(resid)/sqrt(n())
  )
```

Lets take a look at the residuals to do with what the building type is.

```{r building type residuals}
train %>%
    group_by(BldgType) %>%
    summarise(
      number = n(),
      mean_resid = mean(resid),
      se_resid = sd(resid)/sqrt(n())
    )

train %>%
    group_by(MSSubClass) %>%
    summarise(
      number = n(),
      mean_resid = mean(resid),
      se_resid = sd(resid)/sqrt(n())
    )

train %>%
    group_by(HouseStyle) %>%
    summarise(
      number = n(),
      mean_resid = mean(resid),
      se_resid = sd(resid)/sqrt(n())
    )
```

Lets take a look at the residuals to do with the quality of the property

```{r property quality residual plot}
binnedplot(train$OverallQual, train$resid)
binnedplot(train$OverallCond, train$resid)
binnedplot(train$Functional, train$resid)
```

Lets take a look at the residuals to do with the year that the property was built.

```{r year residual plots}
binnedplot(train$YearBuilt, train$resid)
binnedplot(train$YearRemodAdd, train$resid)
```

Lets take a look at the residuals to do with what time the property was sold.

```{r time sold residual plot}
binnedplot(train$YrSold + train$MoSold/12, train$resid)
```


Now lets take a look at residuals for other variables:

```{r misc features residuals}
train %>%
    group_by(RoofStyle) %>%
    summarise(
      number = n(),
      mean_resid = mean(resid),
      se_resid = sd(resid)/sqrt(n())
    )

train %>%
    group_by(Exterior1st) %>%
    summarise(
      number = n(),
      mean_resid = mean(resid),
      se_resid = sd(resid)/sqrt(n())
    )

train %>%
    group_by(MasVnrType) %>%
    summarise(
      number = n(),
      mean_resid = mean(resid),
      se_resid = sd(resid)/sqrt(n())
    )

train %>%
    group_by(Foundation) %>%
    summarise(
      number = n(),
      mean_resid = mean(resid),
      se_resid = sd(resid)/sqrt(n())
    )

train %>%
    group_by(Heating) %>%
    summarise(
      number = n(),
      mean_resid = mean(resid),
      se_resid = sd(resid)/sqrt(n())
    )

train %>%
    group_by(HeatingQC) %>%
    summarise(
      number = n(),
      mean_resid = mean(resid),
      se_resid = sd(resid)/sqrt(n())
    )

train %>%
    group_by(CentralAir) %>%
    summarise(
      number = n(),
      mean_resid = mean(resid),
      se_resid = sd(resid)/sqrt(n())
    )

train %>%
    group_by(Electrical) %>%
    summarise(
      number = n(),
      mean_resid = mean(resid),
      se_resid = sd(resid)/sqrt(n())
    )

binnedplot(train$GarageArea, resid)

train %>%
  filter(PoolArea != 0) %>%
  ggplot(aes(x = PoolArea, y = resid)) +
  geom_point()

train %>%
  filter(MiscVal != 0) %>%
  ggplot(aes(x = MiscVal, y = resid)) +
  geom_point()

train %>%
    group_by(SaleType) %>%
    summarise(
      number = n(),
      mean_resid = mean(resid),
      se_resid = sd(resid)/sqrt(n())
    )
```